What the hell is the title of this paper?

### 2018-05-14 NIPS 2018/main.tex
Remove thm2 + moved RW

\begin{restatable}{theorem}{thmmv} \label{th:mmv}
Let $V$ be the fixed-point of the optimal Bellman operator $T$, and $Q$ the corresponding action-value function. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{V}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}). Let $\nu$ be a probability measure over the state-space. Then, for any $p \geq 1$:
\begin{equation}
\norm{V-\wt{V}}_{\nu,p}^p \leq\ \frac{2R_{max}}{(1-\gamma)^2}\norm{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g}}}_{\nu,p}^p
\end{equation}
\end{restatable}

\begin{restatable}{theorem}{thmm} \label{th:mm}
Let $Q^*$ be the fixed-point of the optimal Bellman operator $T$. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}). Let $\nu$ be a probability measure over the state-action space. Then, for any $p \geq 1$:
\begin{equation}
\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p
\end{equation}
\end{restatable}

@@

\thmmv*
\begin{proof}
We begin by noticing that:
\begin{align*}
\norm{V-\wt{V}}_{\nu,p}^p =\ & \norm{TV - \wt{T}\wt{V}}_{\nu,p}^p \\ =\ &
\norm{TV - \wt{T}V + \wt{T}V - \wt{T}\wt{V}}_{\nu,p}^p \\ \leq\ &
\norm{TV - \wt{T}V}_{\nu,p}^p + \norm{\wt{T}V - \wt{T}\wt{V}}_{\nu,p}^p \\ \leq\ &
\norm{TV - \wt{T}V}_{\nu,p}^p + \gamma\norm{V - \wt{V}}_{\nu,p}^p
\end{align*}
where the first inequality follows from Minkowsky's inequality and the second one from the contraction property of the mellow Bellman operator. This implies that:
\begin{align} \label{eq:mm1}
\norm{V-\wt{V}}_{\nu,p}^p \leq \frac{1}{1-\gamma}\norm{TV - \wt{T}V}_{\nu,p}^p
\end{align}
Let us bound the norm on the right-hand side separately. In order to do that, we will bound the function $\abs{TV(s) - \wt{T}V(s)}$ point-wisely for any state $s$. By applying the definition of the optimal and mellow Bellman operators, we obtain:
\begin{align*}
\abs{TV(s) - \wt{T}V(s)} =\ & \abs{\max_{a}\lbrace R(s,a) + \gamma\mathbb{E}\left[V(s')\right] \rbrace - \mm_{a}\lbrace R(s,a) + \gamma\mathbb{E}\left[V(s')\right] \rbrace}\\ =\ & \abs{\max_a Q(s,a) - \mm_a Q(s,a)}
\end{align*}
Recall that applying the mellow-max is equivalent to computing an expectation under a Boltzmann distribution with inverse temperature $\beta$ induced by $\kappa$ \cite{}\todo{Cite MM}. Thus, we can write:
\begin{align} \label{eq:mm2}
\abs{\max_a Q(s,a) - \mm_a Q(s,a)} =\ & \abs{\sum_a \pi^*(a|s)Q(s,a) - \sum_a \pi_{\beta}(a|s)Q(s,a)}\notag\\ =\ & \abs{\sum_a Q(s,a) \left( \pi^*(a|s) - \pi_{\beta}(a|s)  \right)}\notag\\ \leq\ & \sum_a \abs{Q(s,a)} \abs{\pi^*(a|s) - \pi_{\beta}(a|s)}\notag\\ \leq\ & \frac{R_{max}}{1-\gamma}\sum_a\abs{\pi^*(a|s) - \pi_{\beta}(a|s)}
\end{align}
where $\pi^*$ is the optimal (deterministic) policy w.r.t. $Q$ and $\pi_{\beta}$ is the Boltzmann distribution induced by $Q$ with inverse temperature $\beta$:
\begin{align*}
\pi_{\beta}(a|s) = \frac{e^{\beta Q(s,a)}}{\sum_{a'}e^{\beta Q(s,a')}}
\end{align*}
Denote by $a_1(s)$ the optimal action for state $s$ under $Q$. We can then write:
\begin{align} \label{eq:mm3}
\sum_a\abs{\pi^*(a|s) - \pi_{\beta}(a|s)} =\ & \abs{\pi^*(a_1(s)|s) - \pi_{\beta}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi^*(a|s) - \pi_{\beta}(a|s)}\notag\\ =\ & \abs{1 - \pi_{\beta}(a_1(s)|s)} + \sum_{a \neq a_1(s)}\abs{\pi_{\beta}(a|s)}\notag\\ =\ & 2\abs{1 - \pi_{\beta}(a_1(s)|s)}
\end{align}
Finally, let us bound this last term:
\begin{align} \label{eq:mm4}
\abs{1 - \pi_{\beta}(a_1(s)|s)} =\ & \abs{1 - \frac{e^{\beta Q(s,a_1(s))}}{\sum_{a'}e^{\beta Q(s,a')}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta \left( Q(s,a_1(s)) - Q(s,a_2(s)) \right)}}{\sum_{a'}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta g(s)}}{\sum_{a'}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ =\ & \abs{1 - \frac{e^{\beta g(s)}}{e^{\beta g(s)} + \sum_{a' \neq a_1(s)}e^{\beta \left( Q(s,a') - Q(s,a_2(s))\right)}}}\notag\\ \leq & \abs{1 - \frac{e^{\beta g(s)}}{e^{\beta g(s)} + \abs{\mathcal{A}}}}\notag\\ = & \abs{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g(s)}}}
\end{align}
Combining Eq. \eqref{eq:mm2}, \eqref{eq:mm3}, and \eqref{eq:mm4}, we obtain:
\begin{align*}
\abs{\max_a Q(s,a) - \mm_a Q(s,a)} \leq\ \frac{2R_{max}}{1-\gamma}\abs{1 - \frac{1}{1 + \abs{\mathcal{A}}e^{-\beta g(s)}}}
\end{align*}
Taking the norm and plugging this into Eq. \eqref{eq:mm1} concludes the proof.
\end{proof}

>>>>

\begin{restatable}{theorem}{thmm} \label{th:mm}
Let $Q^*$ be the fixed-point of the optimal Bellman operator $T$. Define the action-gap function $g(s)$ as the difference between the value of the best action and the second best action at each state $s$. Let $\wt{Q}$ be the fixed-point of the mellow Bellman operator $\wt{T}$ with parameter $\kappa > 0$ and denote by $\beta_{\kappa} > 0$ the inverse temperature of the induced Boltzmann distribution (as in \cite{asadi2017alternative}). Let $\nu$ be a probability measure over the state-action space. Then, for any $p \geq 1$:\todo{Correct measure on the rhs}
\begin{equation}
\norm{Q^*-\wt{Q}}_{\nu,p}^p \leq\ \frac{2\gamma R_{max}}{(1-\gamma)^2}\norm{\frac{1}{1 + \frac{1}{\abs{\mathcal{A}}}e^{\beta_{\kappa} g}}}_{\nu,p}^p
\end{equation}
\end{restatable}

@@
